### 2022-08-05 paper/Appendices/AppendixA.tex
update dataset
update paper

\section{Dataset}

\begin{figure}[!h]
	\centering
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/00.apoll.png}
		\caption{apoll}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/01.arm.png}
		\caption{arm}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/02.armadillo.png}
		\caption{armadillo}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/03.bearded-guy.png}
		\caption{bearded-guy}
	\end{subfigure}

@@

	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/16.dresdner-knabe.png}
		\caption{Dresdner-knabe}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/17.fantasy-dragon.png}
		\caption{fantasy-dragon}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/18.fox-skull.png}
		\caption{fox-skull}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/19.garuda-and-vishnu.png}
		\caption{Garuda and Vishnu}
	\end{subfigure}

@@

	\label{fig:dataset_a}
\caption{Point clouds in training dataset A }
\end{figure}
\begin{figure}[!h]
	\centering
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/24.indonesian-statue.png}
		\caption{indonesian-statue}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/25.industrial-compressor.png}
		\caption{industrial-compressor}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/26.kylix.png}
		\caption{kylix}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/27.lobster.png}
		\caption{lobster}
	\end{subfigure}

@@

@@

	\label{fig:dataset_b}
	\caption{Point clouds in training dataset B}
\end{figure}

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/48.guang-base.png}
		\caption{guang-base}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/49.guang-lid.png}
		\caption{guang-lid}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test-dataset/00.garfield.png}
		\caption{Garfield}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test-dataset/01.Bus.png}
		\caption{bus}
	\end{subfigure}

	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test-dataset/02.dragon.png}
		\caption{dragon}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test-dataset/03.baoshanlu.png}
		\caption{baoshanlu}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test-dataset/04.washington.png}
		\caption{Washington}
	\end{subfigure}
	\label{fig:dataset_c}
	\caption{Point clouds in training dataset C}
\end{figure}

\section{How do I change the colors of links?}

The color of links can be changed to your liking using:

{\small\verb!\hypersetup{urlcolor=red}!}, or

{\small\verb!\hypersetup{citecolor=green}!}, or

{\small\verb!\hypersetup{allcolor=blue}!}.

\noindent If you want to completely hide the links, you can use:

{\small\verb!\hypersetup{allcolors=.}!}, or even better:

{\small\verb!\hypersetup{hidelinks}!}.

\noindent If you want to have obvious links in the PDF but not the printed text, use:

{\small\verb!\hypersetup{colorlinks=false}!}.

>>>>

\section{Dataset}
%% dataset a
\begin{figure}
	\centering
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/00.apoll.png}
		\caption{apoll}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/01.arm.png}
		\caption{arm}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/02.armadillo.png}
		\caption{armadillo}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/03.bearded-guy.png}
		\caption{bearded-guy}
	\end{subfigure}

@@

	\label{fig:dataset_a}
\caption{Point clouds in training dataset A }
\end{figure}

%% dataset b 
\begin{figure}
	\centering
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/16.dresdner-knabe.png}
		\caption{Dresdner-knabe}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/17.fantasy-dragon.png}
		\caption{fantasy-dragon}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/18.fox-skull.png}
		\caption{fox-skull}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/19.garuda-and-vishnu.png}
		\caption{Garuda and Vishnu}
	\end{subfigure}

@@

		\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/24.indonesian-statue.png}
		\caption{indonesian-statue}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/25.industrial-compressor.png}
		\caption{industrial-compressor}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/26.kylix.png}
		\caption{kylix}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/27.lobster.png}
		\caption{lobster}
	\end{subfigure}

@@

	\label{fig:dataset_b}
	\caption{Point clouds in training dataset B }
\end{figure}

%% dataset c 
\begin{figure}
	\centering

@@

	\begin{subfigure}[b]{0.23\linewidth}
	\includegraphics[width=\linewidth]{./Figures/train-dataset/48.guang-base.png}
	\caption{guang-base}
\end{subfigure}
\begin{subfigure}[b]{0.23\linewidth}
	\includegraphics[width=\linewidth]{./Figures/train-dataset/49.guang-lid.png}
	\caption{guang-lid}
\end{subfigure}
\begin{subfigure}[b]{0.23\linewidth}
	\includegraphics[width=\linewidth]{./Figures/test-dataset/00.garfield.png}
	\caption{Garfield}
\end{subfigure}
\begin{subfigure}[b]{0.23\linewidth}
	\includegraphics[width=\linewidth]{./Figures/test-dataset/01.Bus.png}
	\caption{bus}
\end{subfigure}

\begin{subfigure}[b]{0.23\linewidth}
	\includegraphics[width=\linewidth]{./Figures/test-dataset/02.dragon.png}
	\caption{dragon}
\end{subfigure}
\begin{subfigure}[b]{0.23\linewidth}
	\includegraphics[width=\linewidth]{./Figures/test-dataset/03.baoshanlu.png}
	\caption{baoshanlu}
\end{subfigure}
\begin{subfigure}[b]{0.23\linewidth}
	\includegraphics[width=\linewidth]{./Figures/test-dataset/04.washington.png}
	\caption{Washington}
\end{subfigure}

	\label{fig:dataset_c}
	\caption{Point clouds in training dataset C}
\end{figure}

\section {More Visualization}

%% gcnn-Visual-more
\begin{figure}
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_point_cloud_noise.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_normal_GCNN-GCNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_error_GCNN-GCNN.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_input.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_GT.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_GCNN-GCNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_error_GCNN-GCNN.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_point_cloud_noise.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_normal_GCNN-GCNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_error_GCNN-GCNN.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_input.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_GT.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_GCNN-GCNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_error_GCNN-GCNN.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_point_cloud_noise.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_normal_GCNN-GCNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_error_GCNN-GCNN.png}

	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_input.png}
		\caption{Input}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_GT.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_GCNN-GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_error_GCNN-CNN.png}
		\caption{Error}
	\end{subfigure}

	\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}
	\decoRule
	\caption{GCNN models evaluation on objects Baoshanlu, Washington statue, Bus(from top to bottom).}
	\label{fig:gcnn-eval-more}
\end{figure}

%% Trip-Net more evaluation
\begin{figure}
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_point_cloud_noise.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_normal_an2-8-1000.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_error_an2-8-1000.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_input.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_GT.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_an2-8-1000.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_error_an2-8-1000.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_point_cloud_noise.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_normal_an2-8-1000.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_error_an2-8-1000.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_input.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_GT.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_an2-8-1000.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_error_an2-8-1000.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_point_cloud_noise.png}

	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_groundtruth.png}

	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_normal_an2-8-1000.png}

	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_error_an2-8-1000.png}

	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_input.png}
		\caption{Input}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_GT.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_an2-8-1000.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_error_an2-8-1000.png}
		\caption{Error}
	\end{subfigure}

	\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Evaluation on objects Baoshanlu, Washington statue, Bus(from top to bottom).}
	\label{fig:trip-net-eval-more}
\end{figure}
